Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-01-23 manuscript/climate_sensitivity_draft.Rmd
add Zuleta ref as counter-example to height trend

One fundamental question regarding forest responses to drought is what drives the observed tendency for large trees to suffer more during drought. @bennett_larger_2015 was the first to show greater growth reductions for larger trees on a global scale, and numerous subsequent studies have reinforced this finding (*e.g.*, @stovall_tree_2019; @hacket-pain_consistent_2016]. However, it has yet to be resolved which of several potential underlying mechanisms drive this pattern. First, taller trees have a greater biophysical challenge of lifting water greater distances against the effects of gravity and friction [@mcdowell_relationships_2011; @mcdowell_darcys_2015; @ryan_hydraulic_2006; @couvreur_water_2018], especially during drought [@zhang_size-dependent_2009]. Second, larger trees may have lower drought resistance because of their higher crown positions, where they are exposed to higher solar radiation, greater wind speeds, and lower humidity [@koike_leaf_2001; @kunert_revised_2017 **REFS-KAT**). Subcanopy trees subsequently tend to fare better specifically due to the benefits of a buffered environment [@pretzsch_drought_2018]. Potentially counteracting the biophysical challenges faced by large trees, their larger root systems confer a potential advantage in terms of allowing greater access to water; however, it appears that this effect is usually insufficient to offset the costs of height and/or crown exposure. 
*A final mechanism that could mediate tree size-related responses to drought is how hydraulic traits are distributed with respect to size [@meakem_role_2018; @liu_hydraulic_2019 [Roskilly et al. 2019](https://www.pnas.org/content/pnas/early/2019/06/14/1900734116.full.pdf)]. **{LS:—larger trees may have larger xylem conduits, which in turn may have less resistance to air seeding and subsequent embolism (Mark Olsen argument, right?) }** The pattern observed by @bennett_larger_2015 could be caused if the larger size classes were dominated by species less adapted to handle drought. Alternatively, larger size classes may be dominated by species that are inherently better adapted to greater biophysical challenges--as is the case in tropical moist forests of Panama, where larger size classes contain greater proportions of deciduous species [@condit_quantifying_2000; @meakem_role_2018]. Understanding the mechanisms driving the greater growth reductions of larger trees during drought will require sorting out the interactive effects of height, canopy position, soil water availability, and species' traits. * {see Lawren's comment on order of presentation}

>>>>

One fundamental question regarding forest responses to drought is what drives the observed tendency for large trees to suffer more during drought. @bennett_larger_2015 was the first to show greater growth reductions for larger trees on a global scale, and numerous subsequent studies have reinforced this finding (*e.g.*, @stovall_tree_2019; @hacket-pain_consistent_2016], although there are exceptions [@zuleta_drought-induced_2017]. However, it has yet to be resolved which of several potential underlying mechanisms drive this pattern. First, taller trees have a greater biophysical challenge of lifting water greater distances against the effects of gravity and friction [@mcdowell_relationships_2011; @mcdowell_darcys_2015; @ryan_hydraulic_2006; @couvreur_water_2018], especially during drought [@zhang_size-dependent_2009]. Second, larger trees may have lower drought resistance because of their higher crown positions, where they are exposed to higher solar radiation, greater wind speeds, and lower humidity [@koike_leaf_2001; @kunert_revised_2017 **REFS-KAT**). Subcanopy trees subsequently tend to fare better specifically due to the benefits of a buffered environment [@pretzsch_drought_2018]. Potentially counteracting the biophysical challenges faced by large trees, their larger root systems confer a potential advantage in terms of allowing greater access to water; however, it appears that this effect is usually insufficient to offset the costs of height and/or crown exposure. 
*A final mechanism that could mediate tree size-related responses to drought is how hydraulic traits are distributed with respect to size [@meakem_role_2018; @liu_hydraulic_2019 [Roskilly et al. 2019](https://www.pnas.org/content/pnas/early/2019/06/14/1900734116.full.pdf)]. **{LS:—larger trees may have larger xylem conduits, which in turn may have less resistance to air seeding and subsequent embolism (Mark Olsen argument, right?) }** The pattern observed by @bennett_larger_2015 could be caused if the larger size classes were dominated by species less adapted to handle drought. Alternatively, larger size classes may be dominated by species that are inherently better adapted to greater biophysical challenges--as is the case in tropical moist forests of Panama, where larger size classes contain greater proportions of deciduous species [@condit_quantifying_2000; @meakem_role_2018]. Understanding the mechanisms driving the greater growth reductions of larger trees during drought will require sorting out the interactive effects of height, canopy position, soil water availability, and species' traits. * {see Lawren's comment on order of presentation}
